Subsegmental language detection in Celtic language text

### 2014-05-08 codeswitch-cltw-2014/codeswitch.tex
hmm
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52623 72bbbca6-d526-0410-a7d9-f06f51895060
add seg
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52624 72bbbca6-d526-0410-a7d9-f06f51895060
testing
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52625 72bbbca6-d526-0410-a7d9-f06f51895060
minocha-try2
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52626 72bbbca6-d526-0410-a7d9-f06f51895060
start
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52631 72bbbca6-d526-0410-a7d9-f06f51895060

%
% File coling2014.tex
%
% Contact: jwagner@computing.dcu.ie
%%
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

@@

\author{Akshay \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Francis M. Tyers \\
  Giellatekno / CLEAR \\
  UiT Norgga \'arktala\v{s} universitehta  \\
  9017 Romsa (Norway) \\
  {\tt francis.tyers@uit.no} \\}

@@

@@

Authors from countries in which access to word-processing systems is
limited should contact the publication chairs,
Joachim Wagner, Liadh Kelly and Lorraine Goeuriot
(\texttt{firstname.lastname @computing.dcu.ie} respectively),
as soon as possible.

We will make additional instructions available at
\url{http://www.coling-2014.org/call-for-papers.php}. Please check
this website regularly.

>>>>

%Try1: akshay minocha
%
% File coling2014.tex
%
% Contact: jwagner@computing.dcu.ie
%%
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

@@

\author{Akshay Minocha \\
  IIIT Hyderabad  \\
  {\tt akshay.minocha@students.iiit.ac.in} \\\And
  Francis M. Tyers \\
  Giellatekno / CLEAR \\
  UiT Norgga \'arktala\v{s} universitehta  \\
  9017 Romsa (Norway) \\
  {\tt francis.tyers@uit.no} \\}

@@

\cite{lyu2006}

@@

Authors from countries in which access to word-processing systems is
limited should contact the publication chairs,
Joachim Wagner, Liadh Kelly and Lorraine Goeuriot
(\texttt{firstname.lastname @computing.dcu.ie} respectively),
as soon as possible.
Testing
We will make additional instructions available at
\url{http://www.coling-2014.org/call-for-papers.php}. Please check
this website regularly.

\section{Evaluation}

\section{Conclusions}
